9. Sea otters always float on their backs when they eat. These marine mammals dine on animals including mussels, sea urchins, clams, and snails, all while floating on their backs. Their extremely dense fur protects them from the cold waters as they eat.

species:
Enhydra lutris nereis — Southern sea otter or “California” sea otter; ranges in California from San Mateo County in the north to near Santa Barbara County in the south.
Enhydra lutris kenyoni — Northern sea otter; found along the coast of Alaska and Washington.
Enhydra lutris lutris — Russian sea otters; found in the Pacific ocean off the coasts of Russia and Japan.

8. Polar bears look white, but they actually have black skin. Unlike other bears, their fur is transparent and reflects visible light. This allows polar bears, which live in the arctic tundra, to blend in with their snow covered environment.

species:
Ursus maritimus - Sea bear; ranges in, around, or on the ocean-predominantly on the sea ice.

4. Cobras are able to kill with a bite as soon as they are born. Baby cobra venom is just as potent as an adult cobra's venom. Their bite is dangerous because cobras can inject large amounts of venom in a single bite. Cobra venom contains a neurotoxin that affects the central nervous system and can lead to paralysis, respiratory system failure, and death.

species:
Naja genus - snakes; represents around 20 species.
Ophiophagus genus - SouthEast Asian snake; found in the rain forests and plains of India, China, and SouthEast Asia..
Aspidelaps genus - Cape Coral snake; represents the shield cobras.
Boulengerina genus - Water snake; represents the water cobras.
Hemachatus genus - Southern African snake.
Pseudohaje genus - Western and central African snake; found in the trees.
Walterinnesia genus - Middle Eastern snake; found in the Middle East from Egypt to Saudi Arabia.

19. Panda’s must eat 25 – 90 pounds (12-38 kg) of bamboo every day to meet their energy needs.This is because bamboo contains very little nutritional value, so they have to eat it in vast quantities to survive. Although the giant panda possess the digestive system of a carnivore, they have evolved to depend almost entirely on bamboo.

species:
Ailuropoda melanoleuca - Southwest China; found in mainly temperate forests high in the mountains of Southwest China.

